\chapter*{ACKNOWLEDGMENTS}
\begin{paracol}{2}
\hbadness5000

For whatever success I have achieved in the intellectual arena I
am grateful to my father, who taught me about right and
wrong, and to my mother, who instilled in me an excitement
about learning. In the writing of this book my greatest debts
are to Edward H. Crane, president of the Cato Institute, for
building an institution in which I have been able to develop the
knowledge to produce this book and for generously allowing
me time to work on it; and to Tom G. Palmer, whose indispensable advice, critiques, and recommended readings went well beyond the call of duty. I also appreciate the advice on various
parts of the manuscript of Jonathan Adler, Stephen Chapman,
Chris Hocker, Karen Lehrman, Ross Levatter, Deroy Murdock,
Eric O'Keefe, Ralph Raico, Jonathan Rauch, Andrea Rich, and
Mario Rizzo. The book is dedicated to Roy Childs and Don
Caldwell, who could have done it better, and to Stephen H.
Miller.

\switchcolumn
无论我在知识的舞台上取得什么样的成就，都要把感谢送
给我的父亲，是他教我明辨是非；还要感谢我的母亲，是她培
养了我对学习的兴趣。在写这本书的过程当中，我亏欠Edward
H. Crane很多，他作为Cato研究所的所长，一手建立了这个研
究所，在这里我获得并发展出了写作本书的知识和理论，同时
他也很慷慨地给我充分的时间让我写作；我还要感谢Tom G.
Palmer,他给了我很多重要的建议、批评和建议阅读的书单，
这些都超越了他的责任。我还要感谢对草稿的各个部分提出建
议的 Jonathan Adler，Stephen Chapman，Chris Hocker，Karen Lehrman, Ross Levatter, Deroy Murdock, Eric O'Keefe Ralph
Racio，Jonathan Rauch, Andrea Rich，Mario Rizzo。 本书献给
Roy Childs和 Don Caldwell, 他们如果写这本书的话会写得更
好。本书还要献给Stephen H. Miller。

\end{paracol}